OJS ALM

### 2023-05-23 Visuals_Interactives/ojs_alm.qmd

---
title: OJS ALM
date-modified: last-modified
format:
  html:
    grid:
      sidebar-width: 50px
      body-width: 1300px
      margin-width: 100px
      gutter-width: 1.5rem
    self-contained: true
    toc: false 
execute: 
   warning: false
code-fold: true
code-tools: true
---

>>>>

---
title: OJS ALM
date-modified: last-modified
categories: [Simulation,ALM,OJS,Interactive]
page-layout: full
format:
  html:
    grid:
      sidebar-width: 50px
      body-width: 1300px
      margin-width: 100px
      gutter-width: 1.5rem
    self-contained: true
    toc: false 
execute: 
   warning: false
code-fold: true
code-tools: true
---
